ICM testing

### 2022-09-05 Scripts/ASR_stocks.Rmd
All stocks now run
Results are summarized in the pdf in the scripts folder. Results from naive run for all the stocks.

---
title: "ICM testing"
output:
  word_document: 
    reference_docx: template.docx
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

@@

# Choose 5 ICES stocks that we have the necessary data for
#ASR <- read_xlsx("../Data/ASR_2018.xlsx", sheet = "ICES")
ASR <- read.csv("D:/Github/ICM/Data/ICM_data_NE_atlantic_stocks.csv")
datatypes <- unique(gsub(x = names(ASR), pattern = "[^a-zA-Z]", replacement=""))

@@

ASR_long <- ASR_trim %>%
  pivot_longer(!c("Management", "Area", "Order", "Family", "Genus", "Species", "Stock", "Year","Model","Case","Notes")) %>%
  separate(col=name, into=c("type", "age"), sep = "\\.")

@@

# Stocks <- ASR_stocks %>%
#                       dplyr::group_by(Stock, Species, type) %>%
#                       dplyr::summarize(ages=length(unique(age)),
#                                 years=length(unique(Year))) %>%
#                       dplyr::arrange(-years, -ages) %>%
#                       dplyr::filter(!Species=="morhua") %>%
#                       dplyr::distinct(Stock) %>%
#                       dplyr::pull(Stock)
# 
# print(Stocks)
Stocks <- Stocks$Stock
# Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
# Esmarki doesn't work great as it is assessed using a quarterly modle.
Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
# Bring in the data
# Handy import function from the rio package... tricky part was getting the right filename here...
for(i in Stocks){
  print(i)
  ASR_sub <- ASR_long %>%
    dplyr::select(Year, Stock, type, age, value) %>%
    dplyr::filter(Stock==i)

@@

  tst <- icm.sim(years = years,
                 mat.age = age.mat,
                 nm = prop.nat.mort,
                 w.age = weight.age,
                 ages = minage:maxage,
                 rems = rem,
                 fecund = mx,
                 N.end = N.end,
                 pop.model = 'exponential',
                 n.sims = 1000,
                 sd.mat = 0.5,
                 sd.nm = 0.5,
                 sd.wt = 0.5,
                 sd.fecund = 0.5)

>>>>

---
title: "ICM testing"
output:
  pdf_document: default
  html_document: default
  word_document: 
    #reference_docx: template.docx
editor_options:
  chunk_output_type: console
---

@@

# Choose 5 ICES stocks that we have the necessary data for
#ASR <- read_xlsx("../Data/ASR_2018.xlsx", sheet = "ICES")
ASR1 <- read.csv("D:/Github/ICM/Data/ICM_data_NE_atlantic_stocks.csv")
ASR <- read.csv("D:/Github/ICM/Data/ICM_data_NW_atlantic_stocks.csv")
ASR <- rbind(ASR1,ASR)
datatypes <- unique(gsub(x = names(ASR), pattern = "[^a-zA-Z]", replacement=""))

@@

ASR_long <- ASR_trim %>%
  pivot_longer(!c("Management", "Area", "Order", "Family", "Genus", "Species", "Stock", "Year","Meeting_or_reference","Model","Case","Notes")) %>%
  separate(col=name, into=c("type", "age"), sep = "\\.")

@@

# Stocks <- ASR_stocks %>%
#                       dplyr::group_by(Stock, Species, type) %>%
#                       dplyr::summarize(ages=length(unique(age)),
#                                 years=length(unique(Year))) %>%
#                       dplyr::arrange(-years, -ages) %>%
#                       dplyr::filter(!Species=="morhua") %>%
#                       dplyr::distinct(Stock) %>%
#                       dplyr::pull(Stock)
# 
# print(Stocks)
Stocks <- Stocks$Stock
# Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
#Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
# Esmarki doesn't work great as it is assessed using a quarterly modle.
#Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
# Bring in the data
# Handy import function from the rio package... tricky part was getting the right filename here...
for(i in Stocks){
  print(i)
  ASR_sub <- ASR_long %>%
    dplyr::select(Year, Stock, type, age, value) %>%
    dplyr::filter(Stock==i)

@@

  tst <- icm.sim(years = years,
                 mat.age = age.mat,
                 nm = prop.nat.mort,
                 w.age = weight.age,
                 ages = minage:maxage,
                 rems = rem,
                 fecund = mx,
                 N.end = N.end,
                 pop.model = 'exponential',
                 n.sims = 500,
                 sd.mat = 0.5,
                 sd.nm = 0.5,
                 sd.wt = 0.5,
                 sd.fecund = 0.5)
